\section{Releasing a new m23 version}

\subsection{Switch to relase}
\begin{itemize}
	\item Run /mdk/bin/menuStart \Rightarrow fork \Rightarrow moveDevel2Release
\end{itemize}


\subsection{Documentation}
\begin{itemize}
	\item Translate all new and changed texts (/m23/inc/help/* and /m23/inc/i18n/*)
	\item Fretch and merge the files via /mdk/m23helper/gitCloneAndMeldTranslations .
	\item Check for missing I18N variables. Run /mdk/doc/manual/bin/checkForMissingi18n.sh
	\item Manual
	\begin{itemize}
		\item Check, if all parts seem to be there. Run: /mdk/doc/manual/bin/checkForMissingHlp.sh
		\item Check, if all HTML entities are in the HTML to LaTeX translation index. Run: /mdk/doc/manual/bin/checkForMissingHTML2LatexEntities.sh
		\item Check, if there are all screenshots present. Run: /mdk/doc/manual/bin/checkMissingScreenshots.sh
		\item Generate and update the screenshots
		\item Run /mdk/bin/menuStart \Rightarrow doc \Rightarrow manual
		\item Choose the language: \Rightarrow lang. Choose all
		\item Generate the tex files: \Rightarrow text
		\item Optimise the PNGs. \Rightarrow optimisePNGs
		\item Generate PDF and HTML version of the manual: \Rightarrow pdf-html
		\item Upload: \Rightarrow upload
		\item Go back
	\end{itemize}
	\item Development guide
	\begin{itemize}
		\item Add (maybe existing new) LaTeX files
		\item Build the development guide: \Rightarrow devguide
		\item Generate it: \Rightarrow generate
		\item Upload: \Rightarrow upload
	\end{itemize}
\end{itemize}



\subsection{Building the files}
\begin{itemize}
\item Debian packages
	\begin{itemize}
		\item /mdk/bin/menuStart \Rightarrow debs \Rightarrow build
		\item Maybe recreate the UCS extra package: Call quickBuild.sh m23-ucs-extra
		\item Test the packages
		\begin{itemize}
			\item UCS VM (local repository): Call /mdk/ucs/installLocalm23DebsOnUCS to install m23 and create the tar with the unmaintained Debian packages.
			\item UCS VM (online test repository): Copy /mdk/ucs/addUCSTestRepository to the UCS and install m23
			\item Debian: Call /mdk/m23helper/addLocalm23ServerRepository, install m23
		\end{itemize}
		\item Upload the packages, if all seems to be right: \Rightarrow directuplinst
		\item Login into t5, call /var/www/ucs/upload-4.1
	\end{itemize}
\item Server installation ISO
	\begin{itemize}
		\item /mdk/bin/menuStart \Rightarrow serverISO \Rightarrow iso . Exit after building.
		\item Upload: cd /mdk/server; ./up iso.file
	\end{itemize}
\item VirtualBox appliance
	\begin{itemize}
		\item Create a new VM (Linux/Debian, 512 MB Ram, growing VDI 16GB HDD
		\item Change the Network card to Network bridge
		\item Start the VM and "insert" the ISO into the virtual CD drive
		\item Select "English".
		\item Use "m23s" as server name, "test" as password and local network settings.
		\item Choose the automatic partitioning and formating.
		\item Call /mdk/bin/prepareOSForCompression after reboot.
		\item Shutdown the VM
		\item Export it (m23server\_xx.y\_rock.ova) and compress (7zm / 7zr -t7z -m0=lzma -mx=9 -mfb=64 -md=32m -ms=on a m23server\_xx.y\_rock.7z m23server\_xx.y\_rock.ova) the exported files.
	\end{itemize}
\item
	\begin{itemize}
		\item Write a SD card with Raspbian.
		\item Configure /etc/network/interfaces to static IP for eth0.
		\item Boot the Raspberry Pi.
		\item Log into it via SSH (user: pi, password: raspberry)
		\item Run "sudo raspi-config".
		\item Call in the menu "Expand Filesystem", set "Advanced Options" "Memory split" to 16 MB, call "Update".
		\item Reboot.
		\item Enable root access (set password to test): "sudo passwd"
		\item Enable root login for SSH in /etc/ssh/sshd\_config
		\item Log out and log into it via SSH (user: root, password: test)
		\item Use commands from /mdk/m23helper/copyPasteTestm23ServerInstall
		\item /mdk/bin/prepareOSForCompression.
		\item Compress the SD card: dd if=/dev/sdX | 7zr a -t7z -m0=lzma -mx=9 -mfb=64 -md=32m -ms=on -si m23server\_xx.y\_rock-RaPi.7z
	\end{itemize}
\end{itemize}


\subsection{Update the m23admin-offline-copy}
	\begin{itemize}
		\item VM: Start the VM and make sure it's available under 192.168.1.23
		\item Host: Export and transfer a new SQL dump: /mdk/m23helper/m23admin-offline-copy/export-dataset.sh
		\item VM: Import the SQL dump and data files: /mdk/m23helper/m23admin-offline-copy/import.sh
		\item Host: Call /mdk/m23helper/m23admin-offline-copy/dlhttrack to make the offline copy and upload the files to SF.
	\end{itemize}


\subsection{CMS}
\begin{itemize}
	\item Write an article
	\item Create the link files by calling /mdk/doc/CMSLinkCreator.sh for the ISO, OVA and RasPi image.
	\item Check in into Bazaar
	\item Upload the files.
\end{itemize}


\subsection{Announcement}
\begin{itemize}
	\item Prepare the newsletter with /mdk/doc/newsletterGenerator3.sh and send it.
\end{itemize}